---
title: "Shiny APP"
author: "Shashi Chandra''"
date: "4 February 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r asas, echo=FALSE, warning=FALSE, message=FALSE}
library(plotly)
library(tidyr)
library(webshot)
library(datasets)
```

## The Regression Project
###Why Shiny ?
 - This application helps in deploying live projects.
 - This will helps looking through the dataset easier with lesser computations.

###About the Project:
 - The project aims at highlighting the relation in between the various factors in mtcars dataset as they are present and are related to each other .

## How to Use:

###TO use The Shiny App:
- Select one of the factors out of hp, cyl, wt which are going to be the predictors.
- Select the another one which is going to be predicted or with whom relation is to be compared.
- Click the submit button to submit your queries to the server.
 wait for the output ...

## The output parts:
First we get to see the data itself.
```{r gd, comment=""}
head(mtcars[,c('mpg','hp','wt','cyl')])

```

## The regression Part
```{r regmod, comment=""}
#Supposing you selected mpg(y) vs cyl(x)
mod<-lm(mpg~cyl, data = mtcars)
summary(mod)

```

## The plot in Between Variables
```{r twey, warning=FALSE, message=FALSE}
plot_ly(mtcars, x = mtcars$wt, y = mtcars$mpg, mode = "markers",
color = as.factor(mtcars$cyl), size = mtcars$hp)


```

## The Plot in Between all the  variables:
```{r affa ,warning=FALSE, message=FALSE}
plot(mtcars[,c('mpg','hp','cyl','wt')], pch=8, color='red')

```

## The plot in the shiny app:
```{r kjbjac, warning=FALSE,message=FALSE, comment=""}
plot(mtcars$mpg,mtcars$cyl,
         xlab = "Miles Per Gallon", ylab = "Cylinders" ,  main = "Scatter Plot of Predicted and Predictor Variables", pch = 9, 
         col = "red", cex = 1)
```


## Thank YOu!